### 2019-05-22 doc/chapters/introduction.tex
Correct chapter Stainless in introduction.tex

\begin{lstlisting}[caption=Example of verifying the function calculating factorial of an integer number, captionpos=b, language=Scala]
    def factorial(n: Int): Int = {
        require(n >= 0)
        if (n == 0) {
          1
        } else {
          n * factorial(n - 1)
        }
    } ensuring(res => res >= 0)
\end{lstlisting}

The function recursively calculates factorial of an integer number. An input to the function is constrained in \textit{require} with positive value. A result of calculation should be also positive, what will be verified by Stainless.
While compiling Stainless disproves the postcondition and gives the number 17 as a counterexample. A number of type Int is a 32 bit value. That is why the function factorial of 17 causes an overflow and results to a negative value. The program would work correct by changing type of a number to BigInt.
The outcome of Stainless verification of the function factorial is shown bellow.

>>>>

\begin{lstlisting}[caption=Example of verifying the function calculating factorial of an integer number, label=listing:factorial, captionpos=b, language=Scala]
    def factorial(n: Int): Int = {
        require(n >= 0)
        if (n == 0) {
          1
        } else {
          n * factorial(n - 1)
        }
    } ensuring(res => res >= 0)
\end{lstlisting}

The function recursively calculates factorial of an integer number. An input to the function is constrained in \textit{require} with non-negative value. A result of calculation should also be non-negative, what will be verified by Stainless.
While compiling Stainless disproves the postcondition and gives the number 17 as a counterexample. A number of type Int is a 32 bit value. That is why calculating factorial of 17 causes an overflow and results to a negative value. The program would work correct by changing a type of a number to BigInt.
The outcome of Stainless verification of the function factorial from Listing \ref{listing:factorial} is shown bellow.
